Formalizing Stack Safety as a Security Property

### 2021-09-30 submission4/main.tex
Save some space in related work

\paragraphx{Formal Stack Safety on Capability Machines}
%
To our knowledge, the only line of work to date that has attempted
a positive and formal characterization of stack safety
is that of Skorstengaard et al. \cite{SkorstengaardSTKJFP}. Their
StkTokens system enforces stack safety on hardware equipped with
memory capabilities, similar to those used in the Cheri system~\cite{Woodruff+14,Chisnall+15}, but
with additional support for linear capabilities.
They define Stack safety as the conjunction of local state encapsulation (LSE) and
well-bracketed control flow (WBCF).
Informally, LSE means that the current activiation can only access its own frame,
and WBCF means that the topmost frame can only return to
the immediately adjacent frame below. Formally, these properties are defined
with reference to a capability machine with a built-in call stack and call and return
instructions; this machine is proven fully abstract with respect to a more
concrete capability machine, an approach termed ``fully abstract overlay semantics.''
We improve upon Skorstengaard et al. \cite{SkorstengaardSTKJFP} in two significant ways:

@@

ii) Skorstengaard et al. \cite{SkorstengaardSTKJFP}'s fully
  abstract overlay
  semantics rely on the definition of a ``stack-safe-by-construction''
  abstract machine that is closely tied to the underlying machine architecture.
  While the fundamental approach can no doubt be ported to other architectures and enforcement
  schemes, each such port will require a new abstract machine definition whose
  safety-by-construction property must be checked afresh.
  Since we abstract over most of the machine
  state as well as the sealing and return conventions, our properties apply directly
  to a range of architectures, code features, and enforcement mechanisms.
  Moreover, we have implemented extensions such as passing arguments on the stack,
  describing callee-saves registers, and coroutines by making simple modifications
  to our base domain model.

>>>>

\paragraphx{Formal Stack Safety on Capability Machines}
%
To our knowledge, the only line of work to date that has attempted
a positive and formal characterization of stack safety
is that of Skorstengaard et al. \cite{SkorstengaardSTKJFP}. Their
StkTokens system enforces stack safety on hardware equipped with
memory capabilities, similar to those used in the Cheri system~\cite{Woodruff+14,Chisnall+15}, but
with additional support for linear capabilities.
They define Stack safety as the conjunction of local state encapsulation (LSE) and
well-bracketed control flow (WBCF).
Informally, LSE means that the current activation can only access its own frame,
and WBCF means that the topmost frame can only return to
the immediately adjacent frame below. Formally, these properties are defined
with reference to a capability machine with a built-in call stack and call and return
instructions; this machine is proven fully abstract with respect to a more
concrete capability machine, an approach termed ``fully abstract overlay semantics.''
We improve upon Skorstengaard et al. \cite{SkorstengaardSTKJFP} in two significant ways:

@@

ii) Skorstengaard et al. \cite{SkorstengaardSTKJFP}'s fully
  abstract overlay semantics rely on the definition of a ``stack-safe-by-construction''
  abstract machine that is closely tied to the underlying machine architecture.
  While the approach can no doubt be ported to other architectures and enforcement
  schemes, each such port will require a new abstract machine definition whose
  safety-by-construction must be checked afresh.
  Since we abstract over most of the machine state as well as the sealing and return conventions, and
  can support further enhancements such as coroutines,
  our properties apply directly to a range of architectures, code features, and enforcement mechanisms.
